LAGOS lake depth

### 2020-03-20 manuscript/figures.Rmd
separate reporting of bathy predictors and lgus stats

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r 01_predictors, fig.cap = "Table 1: Summary of lake depth predictor variables.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../tables/01_predictors.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{4}

>>>>

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r 01_predictors, fig.cap = "Table 1: Summary of lake depth predictor variables for modelling efforts (and for lakes continent-wide).", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../tables/01_predictors.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{4}

### 2020-03-20 tables/01_predictors.Rmd
separate reporting of bathy predictors and lgus stats

```{r summary_table, eval=TRUE}
library(kableExtra)
suppressMessages(library(dplyr))
library(magrittr)

# setwd("tables")
nearshore <- read.csv("../data/00_geometry/nearshore.csv", 
                      stringsAsFactors = FALSE) %>%
  dplyr::select(llid, buffer_slope = slope_mean)
dt <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  left_join(nearshore, by = c("lagoslakeid" = "llid")) %>%
  dplyr::select(-contains("lagoslakeid"), 
                -contains("lake_nhd"), 
                -contains("lake_huc")) %>%
  tidyr::gather(key = "variable") %>%
  group_by(variable) %>%
  mutate(value = as.numeric(value)) %>%
  mutate(q10 = quantile(value, probs = c(0.1), na.rm = TRUE),
         q25 = quantile(value, probs = c(0.25), na.rm = TRUE),
         q50 = quantile(value, probs = c(0.5), na.rm = TRUE),
         q75 = quantile(value, probs = c(0.75), na.rm = TRUE),
         q90 = quantile(value, probs = c(0.9), na.rm = TRUE), 
         ratio = q90 / q10, 
         n = sum(!is.na(value), na.rm = TRUE)) %>%
  dplyr::filter(!is.na(q50)) %>%
  dplyr::distinct(signif(q10, 2), signif(q25, 2), signif(q50, 2), signif(q75, 2), signif(q90, 2), ratio, n) %>%
  dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
  dplyr::select(variable, 
         q10 = `signif(q10, 2)`,
         q25 = `signif(q25, 2)`,
         q50 = `signif(q50, 2)`,
         q75 = `signif(q75, 2)`,
         q90 = `signif(q90, 2)`,
         q10_q90_ratio = ratio,
         n)#  %>%
  # left_join(dt_units, by = "variable") %>%
  # dplyr::select(variable, units, everything())

@@

# dt <- mutate(dt, pretty = case_when(
#   nchar(units) > 0 ~ paste0(pretty, " (", units, ")"),
#   TRUE ~ pretty), 
#   IQR = paste0(q25, " - ", q75))
dt <- dplyr::select(dt, variable, # Variable = pretty,
                    Median = q50, Q25 = q25, Q75 = q75, n)

@@

```{r predictors_table}
# setwd("figures")
dt <- dt %>%
  dplyr::filter(variable %in% 
              c("lake_meandepth_m", 
              names(readRDS("../data/01_depth_model/depth_training.rds")), 
              "buffer_slope")) %>%
  mutate(n = dt$n[which(dt$variable == "inlake_slope")])

>>>>

```{r summary_table, eval=TRUE}
library(kableExtra)
suppressMessages(library(dplyr))
library(magrittr)
library(stringr)

# setwd("tables")
nearshore <- read.csv("../data/00_geometry/nearshore.csv", 
                      stringsAsFactors = FALSE) %>%
  dplyr::select(llid, buffer_slope = slope_mean)
dt_raw <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  left_join(nearshore, by = c("lagoslakeid" = "llid")) %>%
  dplyr::select(-contains("lagoslakeid"), 
                -contains("lake_nhd"), 
                -contains("lake_huc"))

compute_stats <- function(dt){
  # dt <- dt_raw
  dt <- dt %>%
  tidyr::gather(key = "variable") %>%
  group_by(variable) %>%
  mutate(value = as.numeric(value)) %>%
  mutate(q10 = quantile(value, probs = c(0.1), na.rm = TRUE),
         q25 = quantile(value, probs = c(0.25), na.rm = TRUE),
         q50 = quantile(value, probs = c(0.5), na.rm = TRUE),
         q75 = quantile(value, probs = c(0.75), na.rm = TRUE),
         q90 = quantile(value, probs = c(0.9), na.rm = TRUE), 
         ratio = q90 / q10, 
         n = sum(!is.na(value), na.rm = TRUE)) %>%
  dplyr::filter(!is.na(q50)) %>%
  dplyr::distinct(signif(q10, 2), signif(q25, 2), signif(q50, 2), signif(q75, 2), signif(q90, 2), ratio, n) %>%
  dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
  dplyr::select(variable, 
         q10 = `signif(q10, 2)`,
         q25 = `signif(q25, 2)`,
         q50 = `signif(q50, 2)`,
         q75 = `signif(q75, 2)`,
         q90 = `signif(q90, 2)`,
         q10_q90_ratio = ratio,
         n)#  %>%
  # left_join(dt_units, by = "variable") %>%
  # dplyr::select(variable, units, everything())

@@

  # dt <- mutate(dt, pretty = case_when(
  #   nchar(units) > 0 ~ paste0(pretty, " (", units, ")"),
  #   TRUE ~ pretty), 
  #   IQR = paste0(q25, " - ", q75))
  dt <- dplyr::select(dt, variable, # Variable = pretty,
                      Median = q50, Q25 = q25, Q75 = q75, n)
  dt
}

# compute stats for bathymetry lakes
dt_bathy <- dplyr::filter(dt_raw, lagos_effort == "bathymetry")
dt_bathy <- compute_stats(dt_bathy)
dt_bathy <- data.frame(dt_bathy)
# compute stats for all of lagosus
dt_all <- data.frame(compute_stats(dt_raw))
# interleave
dt_bathy <- bind_cols(dplyr::select(dt_bathy, variable), 
          setNames(
            bind_cols(lapply(names(dt_bathy)[2:5], 
                           function(i) paste0(dt_bathy[,i], 
                                              " (", dt_all[,i], ")"))), 
            names(dt_bathy)[2:5]))

@@

```{r predictors_table}
# setwd("figures")
dt <- dt_bathy %>%
  dplyr::filter(str_detect(variable, 
                           "^lake_|^ws_lake_arearatio|^dist_|_slope")) %>%
  dplyr::filter(!str_detect(variable,
                      "totalarea|islandperimeter|between|buffer100m")) %>%
  mutate(n = dt_bathy$n[which(dt_bathy$variable == "inlake_slope")])
